### 2024-02-18 documentation/thesis/thesis_document.tex
.

The figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

The magnet sensor is mounted on a movable arm, which can move \emph{180}
degrees around the magnet on one axis. To be able to map the full
sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}.

This connectivity makes it possible to make the device compatible with
the unified sensor ecosystem using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the unified sensor firmware offers.

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer a physical \emph{RS232} interface. As with the other sensors, this
interface consists of a \emph{Raspberry Pi Pico} with an additional
level shifter.

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
build configuration. In order to be able to read and correctly interpret
the data from the microcontroller, the serial protocol of the sensor is
implemented in a customised version of the \emph{CustomSensor} class as
shown in listing \ref{lst:CustomSensorClass}.

This software or hardware integration can be conducted on any other
measuring device with a suitable communication interface and a known
protocol thanks to the modular design.

>>>>

The figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_build_3D_full_sphere_sensor_with_visible_magnetic_field_strength_deviations_using_different_shaded_vertices_on_a_sphere.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder. The magnet sensor is mounted on a movable arm, which can move
\emph{180} degrees around the magnet on one axis. To be able to map the
full sphere, the magnet is mounted on a turntable. This permits the
manipulator to move a polar coordinate system.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}. This connectivity
makes it possible to make the device compatible with the unified sensor
ecosystem using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the unified sensor firmware offers.

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer a physical \emph{RS232} interface. As with the other sensors, this
interface consists of a \emph{Raspberry Pi Pico} with an additional
level shifter. The teslameter is connected to the microcontroller using
two free \gls{gpio}s in \gls{uart} mode. The firmware is adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontroller, the serial protocol of the
sensor is implemented in a customised version of the \emph{CustomSensor}
class as shown in listing \ref{lst:CustomSensorClass}. This software or
hardware integration can be conducted on any other measuring device with
a suitable communication interface and a known protocol thanks to the
modular design.
